Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-01 inst/paper/main.tex
2

\mypara{Code Generation.} The more traditional use of \eval is to
execute code that was assembled by the programmer into a string. Here
we show the method \c{plot} for class \c{sback} in package
\c{wsbackfit}, simplified for explanatory purposes. The function takes
a long argument list, the names of which are captured in the list
\c{opt}. The string \c{stub} is composed of a subset of the arguments
passed to this function; the variable is used to construct a call to
\c{base::plot} which will draw a plot. \NOTE{This example is a bit
  messed up. What is var? Does the use of ... in the eval grab the
  arguments of this call? If yes does it not end up with xlab twice?
  HELP}
\begin{lstlisting}
 plot.sback <- function(x,...) {
   opt <- names(list(...))
   stub <- paste(
    ifelse("xlab" %in% opt,"",paste(",xlab=\"",var,"\"",sep="")),
    ifelse("main" %in% opt,"",main.aux),
    ifelse("type" %in% opt,"",",type=\"l\""),
    sep = "")
   plot <- paste("plot(x.data,",stub,",...)", sep = "")
   eval(parse(text=plot))
   ...
\end{lstlisting}

@@

\mypara{Code Loading.}
The combination of \parse and \eval is used to parse text from string
or file and evaluate in a custom environment. This pattern is used by
the \source Core R function to load R code from a file in the current
workspace. This is quite useful for loading functions for interactive
data analysis.

\mypara{Metaprogramming.}
The combination of \eval and \substitute is used to do metaprogramming
in R. \substitute can be used to synthesize ASTs by stitching together
user inputs. \substitute walks over its argument AST and replaces the
symbols with their bindings in the specified environment and returns
this new AST which can then be evaluated in custom environments using
\eval.

>>>>

\mypara{Code Generation.} The more traditional use of \eval is to
execute code that was assembled by the programmer into a string. Here
we show the method \c{plot} for class \c{sback} in package
\c{wsbackfit}, simplified for explanatory purposes. The function takes
a long argument list, the names of which are captured in the list
\c{opt}. The string \c{stub} is composed of a subset of the arguments
passed to this function; the variable is used to construct a call to
\c{base::plot} which will draw a plot. \NOTE{This example is a bit
  messed up. What is var? Does the use of ... in the eval grab the
  arguments of this call? If yes does it not end up with xlab twice?
  HELP}
\begin{lstlisting}
 plot.sback <- function(x,...) {
   opt <- names(list(...))
   stub <- paste(
    ifelse("xlab" %in% opt,"",paste(",xlab=\"",var,"\"",sep="")),
    ifelse("main" %in% opt,"",main.aux),
    ifelse("type" %in% opt,"",",type=\"l\""),
    sep = "")
   plot <- paste("plot(x.data,",stub,",...)", sep = "")
   eval(parse(text=plot))
   ...
\end{lstlisting}
The \parse and \eval combination is used by the the \source function
in the base library to load R code from a file in the current
workspace.

@@
